ZCB Pricing

### 2018-08-06 Draft.tex
bub

$$ \left( \begin{array}{cccccc}
-(1/\Delta t)-pm_{1} & -pd_{1} & 0 & \cdots  & 0 & 0\\
-pu_{2} & -(1/\Delta t)-pm_{2} & -pd_{2} &\cdots & 0 & 0 \\
& -pu_{3} & -(1/\Delta t)-pm_{3} & \cdots & 0 & 0  \\
& \vdots &\vdots & \ddots & \vdots & \vdots \\ 
& 0 & 0 & \cdots & -pu_{n-1} & -(1/\Delta t)-pm_{n-1} \end{array} \right
%
\begin{bmatrix}
B_{i-1,1} \\
B_{i-1,2} \\
\vdots \\
B_{i-1,n-1}
\end{bmatrix} 
\\
=
\left( \begin{array}{cccccc}
-(1/\Delta t)+pm_{1} & pd_{1} & 0 & \cdots  & 0 & 0\\
pu_{2} & -(1/\Delta t)+pm_{2} & pd_{2} &\cdots & 0 & 0 \\
& pu_{3} & 1+b_{3} & \cdots & 0 & 0  \\
& \vdots &\vdots & \ddots & \vdots & \vdots \\ 
& 0 & 0 & \cdots & -pu_{n-1} & -(1/\Delta t+pm_{n-1} \end{array} \right) 
%
\begin{bmatrix}
B_{i,1} \\
B_{i,2} \\
\vdots \\
B_{i,n-1}
\end{bmatrix}
+
\begin{bmatrix}
pu_{1}B_{i-1,0} \\
0 \\
\vdots \\
0 \\
pd_{j-1}B_{i-1,n-1}
\end{bmatrix}
+
 \begin{bmatrix}
pu_{1}B_{i,0} \\
0 \\
\vdots \\
0 \\
pd_{j-1}B_{i,n-1}
\end{bmatrix}  
$$

>>>>

$$ \left( \begin{array}{cccccc}
-(1/\Delta t)-pm_{1} & -pd_{1} & 0 & \cdots  & 0 & 0\\
-pu_{2} & -(1/\Delta t)-pm_{2} & -pd_{2} &\cdots & 0 & 0 \\
& -pu_{3} & -(1/\Delta t)-pm_{3} & \cdots & 0 & 0  \\
& \vdots &\vdots & \ddots & \vdots & \vdots \\ 
& 0 & 0 & \cdots & -pu_{n-1} & -(1/\Delta t)-pm_{n-1} \end{array} \right)
%
\begin{bmatrix}
B_{i-1,1} \\
B_{i-1,2} \\
\vdots \\
B_{i-1,n-1}
\end{bmatrix} 
\\
=
\left( \begin{array}{cccccc}
-(1/\Delta t)+pm_{1} & pd_{1} & 0 & \cdots  & 0 & 0\\
pu_{2} & -(1/\Delta t)+pm_{2} & pd_{2} &\cdots & 0 & 0 \\
& pu_{3} & 1+b_{3} & \cdots & 0 & 0  \\
& \vdots &\vdots & \ddots & \vdots & \vdots \\ 
& 0 & 0 & \cdots & -pu_{n-1} & -(1/\Delta t+pm_{n-1} \end{array} \right) 
%
\begin{bmatrix}
B_{i,1} \\
B_{i,2} \\
\vdots \\
B_{i,n-1}
\end{bmatrix}
+
\begin{bmatrix}
pu_{1}B_{i-1,0} \\
0 \\
\vdots \\
0 \\
pd_{j-1}B_{i-1,n-1}
\end{bmatrix}
+
 \begin{bmatrix}
pu_{1}B_{i,0} \\
0 \\
\vdots \\
0 \\
pd_{j-1}B_{i,n-1}
\end{bmatrix}  
$$
